Manuscript

### 2015-03-13 inst/simulation/manuscript.Rmd
...

iall <- rbind(i, i2000, i10days)
p <- plotIntersectionPopulationSizeTable(iall)
saveFigure(p, "manuscript-figure-4x.png", height=7.87/2.5) # draft quality
saveFigure(p, "manuscript-figure-4x.pdf", height=7.87/2.5, dpi=300)

@@

plotPopulationCorrelations <- function(populationCorrelations, case) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  ggtitle(paste("Case:", case)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.title=element_text(size=10),
                                      plot.margin=unit(c(0, 0, 0, 0), units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

p1 <- plotPopulationCorrelations(pc1, "a")
saveFigure(p1, "manuscript-figure-4a.png")
p2 <- plotPopulationCorrelations(pc2, "b")
saveFigure(p2, "manuscript-figure-4b.png")
p3 <- plotPopulationCorrelations(pc3, "c")
saveFigure(p3, "manuscript-figure-4c.png")
```

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) +
    #scale_colour_manual("Model", values=c("black", "darkgray", "gray"), labels=modelLabels) +
    scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0, 0, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal")
  return(p)
}
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", height=7.87/2, dpi=200)
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[c(1,3,5)], panel="a", scenarioNames=scenarios, cutoff=cutoff)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,5)], panel="b", scenarioNames=scenarios, cutoff=10*cutoff)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,5)], panel="c", scenarioNames=scenarios, cutoff=cutoff)

cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", height=7.87/2, dpi=200)
saveFigure(p, "manuscript-figure-5.pdf", height=7.87/2, dpi=300)
```

>>>>

iall <- rbind(i, i2000, i10days)
p <- plotIntersectionPopulationSizeTable(iall)
saveFigure(p, "manuscript-figure-4x.png", height=7.87/2) # draft quality
saveFigure(p, "manuscript-figure-4x.pdf", height=7.87/2, dpi=300)

@@

plotPopulationCorrelations <- function(populationCorrelations, case) {
  populationCorrelations$Scenario <- prettyScenario(populationCorrelations$Scenario)
  p <- ggplot(populationCorrelations, aes(True, Correlation)) + geom_point(size=1, colour="black") +
  facet_wrap(~Scenario, ncol=2) + xlab("True population size") +
  scale_y_continuous(limits=c(-1,1)) +
  ggtitle(paste("Case:", case)) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                      plot.title=element_text(size=10),
                                      plot.margin=unit(c(0.2, 0, 0, 0), units="line"),
                                      panel.margin=unit(0, units="line"))#, axis.text.x=element_text(angle=45, hjust=.5, vjust=1))
  return(p)
}
```

@@

p1 <- plotPopulationCorrelations(pc1, "Case 1")
saveFigure(p1, "manuscript-figure-4a.png")
saveFigure(p1, "manuscript-figure-4a.pdf", dpi=300)
p2 <- plotPopulationCorrelations(pc2, "Case 2")
saveFigure(p2, "manuscript-figure-4b.png")
saveFigure(p2, "manuscript-figure-4b.pdf", dpi=300)
p3 <- plotPopulationCorrelations(pc3, "Case 3")
saveFigure(p3, "manuscript-figure-4c.png")
saveFigure(p3, "manuscript-figure-4c.pdf", dpi=300)
```

@@

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) +
    scale_colour_manual("Model", values=c("black", "gray26", "gray80"), labels=modelLabels) +
    #scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0.2, 0, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal",
          legend.key.width=unit(.7, "line"))
  return(p)
}
#p <- plotCIProportions(cip)
#saveFigure(p, "manuscript-figure-5.png", height=7.87/2, dpi=200)
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[c(1,3,5)], panel="Case 1", scenarioNames=scenarios, cutoff=cutoff)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,5)], panel="Case 2", scenarioNames=scenarios, cutoff=10*cutoff)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,5)], panel="Case 3", scenarioNames=scenarios, cutoff=cutoff)

cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", height=7.87/2)
saveFigure(p, "manuscript-figure-5.pdf", height=7.87/2, dpi=300)
```
